Trends of downward SDR in Thessaloniki

### 2023-05-05 Article.Rmd
Commit 2023-05-05 22:17

<!-- basic concepts -->
Our method to characterize the sky conditions and the definition of each sky condition has some subjectivity. The algorithm was calibrated with the main focus to identify the presence of clouds on the sky dome, although there are marginal cases that there will be false positives or false negateives.

@@

<!-- measurement -->
We sample the signal of the CM-21 pyranometer with a rate of $1 {Hz}$, and record the average signal and the standard deviation over each minute of the hour.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation bellow $10^\circ$, for a period of $3 h$).
<!-- physical quantities -->
The signal is converted to radiation using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.

>>>>

<!-- basic concepts -->
Our method to characterize the sky conditions and the definition of each sky condition has some subjectivity.
The algorithm was calibrated with the main focus to identify the presence of clouds on the sky dome, although there are marginal cases that there will be false positives or false negatives identifications.

@@

<!-- measurement -->
The signal of the CM-21 pyranometer is sampled with a rate of $1 {Hz}$, and a record the average signal and the standard deviation every one minute is recorded.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation bellow $10^\circ$, for a period of $3 h$).
<!-- physical quantities -->
The signal is converted to radiation using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.
